Dark Control: The Default Mode Network as a Reinforcement Learning Agent

### 2018-08-01 paper/paper.tex
Update title of Figure 3

\begin{figure}[!h]
  \centering
  \includegraphics[width=1.\linewidth]{POMDP_Fig.pdf}
  \caption{\textbf{Reinforcement learning in a nutshell.} Given the current state of the environment,
    the agent takes an action by following the policy matrix as updated by the Bellman equation. The agent receives a triggered reward and observes the next state. The process goes on until interrupted or a goal state is reached.}
  \label{fig:rl}
\end{figure}

>>>>

\begin{figure}[!h]
  \centering
  \includegraphics[width=1.\linewidth]{POMDP_Fig.pdf}
  \caption{\textbf{Illustration of Partially Observable Markov Decision Process (POMDP).} Given the current state of the environment,
    the agent takes an action by following the policy matrix as updated by the Bellman equation. The agent receives a triggered reward and observes the next state. The process goes on until interrupted or a goal state is reached.}
  \label{fig:rl}
\end{figure}
